Query Optimization for Dynamic Imputation

### 2017-03-01 paper/main.tex
Couple edits to results writeup

% results that can be used in any section
\newcommand{\demorows}{10175}
\newcommand{\labexrows}{9813}
\newcommand{\acsbaseresultminutes}{355 minutes}
\newcommand{\acsbaseresulthours}{just under 6 hours}
\newcommand{\acsimputedbzeroresult}{4 seconds}
\newcommand{\acsimputedboneresult}{1 second}
\newcommand{\lowxalphazero}{10}
\newcommand{\lowsmapealphazero}{0}
\newcommand{\highxalphazeroexacs}{200}
\newcommand{\highxalphaoneexacs}{1000}
\newcommand{\highsmapealphaoneexacs}{24}
\newcommand{\highxalphaone}{16000}
\newcommand{\nullv}{NULL}
\newcommand{\planningruntimepercent}{8.5}
\newcommand{\planningmaxtime}{40}

@@

\begin{abstract}
  Missing values abound in data analysis and present a usability challenge.
  Users are forced to pick between removing tuples with missing values or creating a clean duplicate of their data by applying a relatively expensive imputation strategy.
  Our system, \ProjectName{}, incorporates imputation into a cost-based query optimizer, performing necessary imputations on the fly for each query.
  This allows users to immediately explore their data, while the system picks the optimal placement of imputation operations.
  % This placement is based on the specific query issued and a user-provided parameter that trades off data quality and runtime performance.
  % We incorporate the imputation operators into the relational algebra, allowing for traditional optimizations to take place.
  We  evaluate this approach on two real-world survey-based datasets and 
  % from the \textit{Center for Disease Control and Prevention} and \textit{freeCodeCamp}.
  our experiments show that our query plans are between \lowxalphazero{} and \highxalphazeroexacs{} times faster than first imputing the base tables.
  Furthermore, we show that the query results from on-the-fly imputation differ in one error measure from the standard full-table imputation approach by \lowsmapealphazero{}--\highsmapealphaoneexacs{}\%.
  Finally, we show that while dropping tuples with missing values that fail query constraints discards 3--88\% of the data, on-the-fly imputation loses only 0--10\%.
\end{abstract}

>>>>

% results that can be used in any section
\newcommand{\demorows}{10175}
\newcommand{\labexrows}{9813}
\newcommand{\acsbaseresultminutes}{355 minutes}
\newcommand{\acsbaseresulthours}{just under 6 hours}
\newcommand{\acsimputedbzeroresult}{4 seconds}
\newcommand{\acsimputedboneresult}{1 second}
\newcommand{\lowxalphazero}{10}
\newcommand{\lowsmapealphazero}{0}
\newcommand{\highxalphazeroexacs}{200}
\newcommand{\highxalphaoneexacs}{1000}
\newcommand{\highsmapealphaoneexacs}{24}
\newcommand{\highxalphaone}{16000}
\newcommand{\nullv}{NULL}
\newcommand{\planningruntimepercent}{1.8}
\newcommand{\planningmediantime}{1.5}
\newcommand{\planningmaxtime}{34}

@@

\begin{abstract}
  Missing values are common in data analysis and present a usability challenge.
  Users are forced to pick between removing tuples with missing values or creating a cleaned version of their data by applying a relatively expensive imputation strategy.
  Our system, \ProjectName{}, incorporates imputation into a cost-based query optimizer, performing necessary imputations on-the-fly for each query.
  This allows users to immediately explore their data, while the system picks the optimal placement of imputation operations.
  % This placement is based on the specific query issued and a user-provided parameter that trades off data quality and runtime performance.
  % We incorporate the imputation operators into the relational algebra, allowing for traditional optimizations to take place.
  We evaluate this approach on three real-world survey-based datasets and 
  % from the \textit{Center for Disease Control and Prevention} and \textit{freeCodeCamp}.
  our experiments show that our query plans are between \lowxalphazero{} and \highxalphazeroexacs{} times faster than first imputing the base tables.
  Furthermore, we show that the query results from on-the-fly imputation differ from the standard full-table imputation approach by \lowsmapealphazero{}--\highsmapealphaoneexacs{}\%, in one error measure.
  Finally, we show that while dropping tuples with missing values that fail query constraints discards 3--88\% of the data, on-the-fly imputation loses only 0--10\%.
\end{abstract}
